---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Allison Li"
date: "03/26/2025"
output: github_document
---

## Load Packages and Data  

First, let's load the necessary packages:  

```{r load-packages, message = FALSE}
#install.packages("robotstxt")

library(robotstxt)
paths_allowed("https://collections.ed.ac.uk/art)")
library(tidyverse) 
library(skimr)
library(ggplot2)
```

Now, load the dataset. If your data isn't ready yet, you can leave `eval = FALSE` for now and update it when needed.  


```{r load-data, message = FALSE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

## Exercise 9

Let's start working with the **title** column by separating the title and the date:  

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)  
```

looking at the uoe_art dataset, there is the column "link." 

## Exercise 10  

#The warning "Additional pieces discarded in 48 rows..." is suggesting that althought we are seperating the title into title text and date text, some of them have more than these two information. I checked 58 and 85 and these rows have two parentheses, which is why it is showing warning. For exmpale, 85 has a parenthesis showing the condition of the art piece, which is broken. Therefore, it is ok for us to ignore this warning since the data and variables are not affected. 
#The warning "Missing pieces filled with "NA" in 696 rows..." is suggesting that for these rows the original title variable did not have years/ date of the art work in. We can ignore the message since it automatically put "NA" in these cells for the date variable. 


## Exercise 11  

```{r skim of the dataset}
skim(uoe_art)
```

According to the summary, `r sum(is.na(uoe_art$artist))` art pieces have missing artist and `r sum(is.na(uoe_art$year))` has missing years. 

## Exercise 12

```{r histogram}

ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 10, fill = "#fec6df", color = "#a39fe1") +
  scale_x_continuous(limits = range(1800:2020, na.rm = TRUE)) +
  labs(title = "Histogram of Years",
       x = "Year",
       y = "Frequency") +
  theme_minimal()
```

According to the warning, I saw that some of the variables are outside of the year range, which seems a little weird. I went checking the year variable and saw that one piece work had the year as "2" in the variable. Additionally, it seems like 1960s has yielded most of the art pieces on this website. 

## Exercise 13

#As mentioned above, No.2548 has an out-of-the-ordinary year. I went to the website and found that the accurate year is 1964, website link: https://collections.ed.ac.uk/art/record/21649?highlight=*:*. I think our code did not work because there are two parentheses that contains numeric values for this work, and our code chose to scrape the first numeric value, which is not the year. 

```{r corrected year}
## to correct the year, I would want to replace the original value to 1964.
uoe_art_correctyear <- uoe_art %>%
  mutate(
    year = case_when(
    year == 2 ~ 1964,
    TRUE ~ year
    ))

## histogram again
ggplot(uoe_art_correctyear, aes(x = year)) +
  geom_histogram(binwidth = 10, fill = "#fec6df", color = "#a39fe1") +
  labs(title = "Histogram of Years",
       x = "Year",
       y = "Frequency") +
  theme_minimal()

```


##Exercise 14

```{r most mentioned artist}
most_artists <- uoe_art %>%
  count(artist, sort = TRUE) 

print(most_artists)
```

According to the "Unknown" artist, the artist that has the most work in the collection is Emma Gillies. After searching her name, I think it is because that she studied at Edinburgh College of Art and lived in the city for her life. 

##Exercise 15

```{r child count}
child_count <- uoe_art %>%
  filter(str_detect(title, "(?i)child")) %>%
  count()
print(child_count)
```

According to the table, there are 11 work with the word "children" inside.





